Global Optimization of the Analogue Method by Means of Genetic Algorithms

### 2015-01-23 Optimization - Journal of Climate/template.tex
Removal of the sub-lists.

\begin{enumerate}
	\item Manual choice of the following parameters:
	\begin{itemize}
		\item meteorological variable,
		\item atmospheric level,
		\item time frame (hour of observation),
		\item initial analogue numbers.
	\end{itemize}

@@

Calibration is done in stages, to determine the optimal parameters systematically. The steps are distinct and previously optimized parameters are generally not reassessed. \citet{Bontron2004} notes however that ''\textit{this type of algorithm, which is changing the parameters of a model in a unique path, can lead to the best solution, provided that there is no local optima}''. The advantage of this method is that it is fast and has low computing requirements. We added small improvements to this method by allowing the spatial windows to do other moves, such as:

\begin{itemize}
	\item increase in 2 simultaneous directions,
	\item decrease in 1 or 2 simultaneous directions,
	\item expansion or contraction (in every direction),
	\item shift of the window (without resizing) in 8 directions (including diagonals),
	\item and finally all the moves described above, but with a factor of 2, 3, or more. For example, we try to increase by 2 units in one (or more) direction. This allows to skip one size that may not be optimal.
\end{itemize}

@@

	\item \textbf{Roulette wheel weighting}: the roulette technique refers to gambling. But unlike casino roulette, this one is biased. Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}. The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction. There are two techniques for weighting the individuals of the mating pool:
	\begin{itemize}
		\item Roulette wheel weighting on rank: the probability of each individual depends on its rank $n$:
		\begin{equation}
		p_{n}=\dfrac{N_{mp}-n+1}{\sum^{N_{mp}}_{n=1}n}
		\label{equation_mating_rank_weighting}
		\end{equation}

		\item Roulette wheel weighting on fitness: the selection probability is calculated based on the value of the objective function. This approach gives more weight to the best individuals when the distribution of scores is wide, while the weight is almost similar when all individuals have approximately the same score \citep{Haupt2004}. The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
		\begin{equation}
		p_{n}=\frac{score_{n}-score_{N_{mp}}}{\sum_{n=1}^{N_{mp}} (score_{n}-score_{N_{mp}})}
		\label{equation_mating_score_weighting}
		\end{equation}
		In our application, the last individual ($N_{mp}$) has zero probability of being selected.
	\end{itemize}

@@

\begin{itemize}
	\item \textbf{Population size}: we found the following ranges to be accurate in average:
	\begin{itemize}
		\item $50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 atmospheric levels),

		\item $N\approx200$ for a bit more complex method (1 level of analogy with 4 atmospheric levels, or 2 level of analogy with less atmospheric levels),

		\item $N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 atmospheric levels for the atmospheric circulation, and 2 to 4 levels for the analogy humidity),
	\end{itemize}
	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality. However, this cannot be generalized and depends on the analogue method to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.

@@

	\begin{itemize}
		\item Non-uniform mutation \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low. The number of required evaluations, however, can be quite substantial. The main disadvantage of the non-uniform mutation is the complexity of its parameterization, which is difficult to estimate a priori. These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated. We could observe that the $\omega$ coefficient does not influence performance. The role of $G_{max}$ is rather difficult to judge, but does not seem essential. The mutation rate was found to be important. The difficulty is that the optimal value seems to be very case-related. Indeed, by even changing the precipitation time series (ie optimizing for another region), but not the complexity of the analogue method, the optimal mutation rate changes, making it impossible to estimate in advance.

		\item Chromosome of adaptive search radius \citep{Horton2012a}: unlike the previous one, this operator is very robust, as it requires no option and is self-managing. It may be sometimes a little bit less efficient for simple problems, but does not require parameterization, which is an important advantage. It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, eg, the chromosome of adaptive mutation rate).

		\item Multi-scale mutation \citep{Horton2012a}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate. Our tests seem to indicate that a high mutation rate here is preferable.
	\end{itemize}

>>>>

\begin{enumerate}
	\item Manual choice of the following parameters:
	\begin{enumerate}
		\item meteorological variable,
		\item atmospheric level,
		\item time frame (hour of observation),
		\item initial analogue numbers.
	\end{enumerate}

@@

Calibration is done in stages, to determine the optimal parameters systematically. The steps are distinct and previously optimized parameters are generally not reassessed. \citet{Bontron2004} notes however that ''\textit{this type of algorithm, which is changing the parameters of a model in a unique path, can lead to the best solution, provided that there is no local optima}''. The advantage of this method is that it is fast and has low computing requirements. We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), (5) and finally all the moves described above, but with a factor of 2, 3, or more. For example, we try to increase by 2 units in one (or more) direction. This allows to skip one size that may not be optimal.

@@

	\item \textbf{Roulette wheel weighting}: the roulette technique refers to gambling. But unlike casino roulette, this one is biased. Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}. The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction. There are two techniques for weighting the individuals of the mating pool:

	\textit{Roulette wheel weighting on rank}: the probability of each individual depends on its rank $n$:
	\begin{equation}
	p_{n}=\dfrac{N_{mp}-n+1}{\sum^{N_{mp}}_{n=1}n}
	\label{equation_mating_rank_weighting}
	\end{equation}

	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function. This approach gives more weight to the best individuals when the distribution of scores is wide, while the weight is almost similar when all individuals have approximately the same score \citep{Haupt2004}. The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
	\begin{equation}
	p_{n}=\frac{score_{n}-score_{N_{mp}}}{\sum_{n=1}^{N_{mp}} (score_{n}-score_{N_{mp}})}
	\label{equation_mating_score_weighting}
	\end{equation}
	In our application, the last individual ($N_{mp}$) has zero probability of being selected.

@@

\begin{itemize}
	\item \textbf{Population size}: we found the following ranges to be accurate in average:

	$50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 atmospheric levels),

	$N\approx200$ for a bit more complex method (1 level of analogy with 4 atmospheric levels, or 2 level of analogy with less atmospheric levels),

	$N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 atmospheric levels for the atmospheric circulation, and 2 to 4 levels for the analogy humidity),

	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality. However, this cannot be generalized and depends on the analogue method to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.

@@

	\textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low. The number of required evaluations, however, can be quite substantial. The main disadvantage of the non-uniform mutation is the complexity of its parameterization, which is difficult to estimate a priori. These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated. We could observe that the $\omega$ coefficient does not influence performance. The role of $G_{max}$ is rather difficult to judge, but does not seem essential. The mutation rate was found to be important. The difficulty is that the optimal value seems to be very case-related. Indeed, by even changing the precipitation time series (ie optimizing for another region), but not the complexity of the analogue method, the optimal mutation rate changes, making it impossible to estimate in advance.

	\textit{Chromosome of adaptive search radius} \citep{Horton2012a}: unlike the previous one, this operator is very robust, as it requires no option and is self-managing. It may be sometimes a little bit less efficient for simple problems, but does not require parameterization, which is an important advantage. It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, eg, the chromosome of adaptive mutation rate).

	\textit{Multi-scale mutation} \citep{Horton2012a}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate. Our tests seem to indicate that a high mutation rate here is preferable.
